Deep Learning

### 2015-01-13 deepreview.tex
stub for missing fig:imagenet-output

The first major application of this pre-training approach was in speech
recognition and it was made possible by the advent of fast Graphics
Processing Units (GPUs) that were convenient to program~\citep{RainaICML09-small}.  
In 2009, the approach was used to map short temporal windows of coefficients extracted
from a soundwave to a set of probabilities for the various fragments of
speech that might be represented by the frame in the center of the window.
It achieved record-breaking results on a standard speech recognition
benchmark that used a small vocabulary~\citep{TIMITpaper} and was quickly
developed to give record-breaking results on a large vocabulary
task~\citep{Dahl2012}.  By 2012, versions of the deep net from 2009 were being
developed by many of the major speech groups\citep{Hinton-et-al-2012} and were already
being deployed in Android phones.  For smaller datasets, unsupervised
pre-training helps to prevent overfitting~\citep{Erhan+al-2010-small}, 
leading to significantly better generalization when the number of
labeled examples is small. Once deep
learning had been rehabilitated, it turned out that large labeled datasets
did not need the pre-training stage, provided the scales of the initial
random weights were carefully chosen to avoid very large or very small
initial gradients.

Interest in recurrent networks (which are deep in time) was revived by
``Long Short Term Memory'' networks (LSTMs) that use special hidden units
whose natural behaviour is to remember inputs for a long
time~\citep{Hochreiter+Schmidhuber-1997}.  
A linear ``memory cell'' interacts with other units
via gated connections whose weights are multiplied by the state of a
logistic gating unit that has an activation between $0$ and $1$. The input
vector has little effect on the state of that cell if the cell's input
gate has a low activation so memory cells can learn to selectively ignore
the input.  Similarly, a memory cell has little effect on the output if its
output gate has low activation. Each memory cell also has a connection to
itself (it is a leaky neuron) at the next time-step that has a weight of 1 so it tends to copy its
own real-valued state, but this self-connection is gated by a ``keep gate'' so
the stored value leaks quickly unless the keep-gate has an activation
near $1$.  The gates themselves have their activities determined by
weighted inputs that they receive from the input vectors and all of the
memory cells.

When LSTMs were first described % in English
\citep{Hochreiter+Schmidhuber-1997} their complexity was off-putting
and, despite their impressive ability to learn very long-range temporal
structure on toy problems, they were largely ignored until they achieved
excellent results in a competition to read cursive
hand-writing~\citep{Graves-et-al-2009}. They have subsequently proved to be very
effective for tasks that have sequential input.  They are now better than
deep feed-forward networks for speech recognition~\citep{Graves-et-al-ICASSP2013} and
unlike feed-forward nets they can implement an entire speech recognition
system that goes all the way from coefficents derived from the soundwave to
the sequence of characters in the transcription.  They
are also what is currently used for the encoder and decoder networks that
perform so well at machine
translation~\citep{Bahdanau-et-al-arxiv2014,Sutskever-et-al-NIPS2014}.

Recent work~\citep{Chung-et-al-NIPSDL2014-small,Yao-et-al-SLU-workshop2014} 
suggests that not all the elements of the LSTM
architecture are required, the crucial element being the presence and learnability 
of the so-called forget gate, controlling the leaking rate (or time constant) of the cell.
%It is not yet clear which aspects of the complicated architecture of LSTMs
%are really necessary. Memory cells are a good way of allowing the
%backpropagated error derivatives to neither explode nor vanish, but they
%are not the only way.  For example, recurrent nets with rectified linear
%hidden units that use the non-linear function $y=max(0,x)$ are much simpler
%than LSTMs and if the recurrent weight matrix is initialized to be close to
%the identity matrix they work about as well as LSTMs both for toy problems
%involving very long-range temporal structure and for real tasks like
%predicting the next word in text\citep{LeHinton}.

@@

>>>>

The first major application of this pre-training approach was in speech
recognition and it was made possible by the advent of fast Graphics
Processing Units (GPUs) that were convenient to
program~\citep{RainaICML09-small}.  In 2009, the approach was used to map
short temporal windows of coefficients extracted from a soundwave to a set
of probabilities for the various fragments of speech that might be
represented by the frame in the center of the window.  It achieved
record-breaking results on a standard speech recognition benchmark that
used a small vocabulary~\citep{TIMITpaper} and was quickly developed to
give record-breaking results on a large vocabulary task~\citep{Dahl2012}.
By 2012, versions of the deep net from 2009 were being developed by many of
the major speech groups~\citep{Hinton-et-al-2012} and were already being
deployed in Android phones.  For smaller datasets, unsupervised
pre-training helps to prevent overfitting~\citep{Erhan+al-2010-small},
leading to significantly better generalization when the number of labeled
examples is small, or in a transfer setting, i.e., when we have lots of
examples for some ``source'' tasks but very few for some ``target''
task. In this context, unsupervised representation learning helped to win
several transfer learning
competitions~\citep{UTLC+LISA-2011-small,Goodfellow-icml2012}.  Once deep
learning had been rehabilitated, it turned out that large labeled datasets
did not need the pre-training stage, provided the scales of the initial
random weights were carefully chosen to avoid very large or very small
initial gradients~\citep{GlorotAISTATS2010-small} and that even better
results (especially for very deep networks)
could be obtained by using rectifying non-linearities rather than
sigmoid or tanh
non-linearities~\citep{Glorot+al-AI-2011-small,Krizhevsky-2012-small}.

Interest in recurrent networks (which are deep in time) was revived by
``Long Short Term Memory'' networks (LSTMs) that use special hidden units
whose natural behaviour is to remember inputs for a long
time~\citep{Hochreiter+Schmidhuber-1997}.  
A linear ``memory cell'' interacts with other units
via gated connections whose weights are multiplied by the state of a
logistic gating unit that has an activation between $0$ and $1$. The input
vector has little effect on the state of that cell if the cell's input
gate has a low activation so memory cells can learn to selectively ignore
the input.  Similarly, a memory cell has little effect on the output if its
output gate has low activation. Each memory cell is a gated leaky neuron, i.e.,
it also has a connection to
itself at the next time-step that has a weight of 1 (so it tends to copy its
own real-valued state and accumulate the external signal), 
but this self-connection is {\em gated} by a ``forget gate'' so
the stored value leaks quickly unless the forget gate has an activation
near $1$.  The gates themselves have their activities determined by
weighted inputs that they receive from the input vectors and all of the
memory cells.

When LSTMs were first described % in English
\citep{Hochreiter+Schmidhuber-1997},
their complexity might have been off-putting
and, despite their impressive ability to learn very long-range temporal
structure on toy problems, they were largely ignored until they achieved
excellent results in a competition to read cursive
hand-writing~\citep{Graves-et-al-2009}. They have subsequently proved to be very
effective for tasks that have sequential input.  Combined with depth of
representation, they are now better than
deep feed-forward networks for speech recognition~\citep{Graves-et-al-ICASSP2013} and
unlike feed-forward nets they can implement an entire speech recognition
system that goes all the way from coefficents derived from the soundwave to
the sequence of characters in the transcription.  LSTMs or related forms of gated
units are also what is currently used for the encoder and decoder networks that
perform so well at machine
translation~\citep{Bahdanau-et-al-arxiv2014,Sutskever-et-al-NIPS2014}.

Recent work~\citep{Chung-et-al-NIPSDL2014-small,Yao-et-al-SLU-workshop2014} 
suggests that not all the elements of the LSTM
architecture are required, the crucial element being the presence and learnability 
of the forget gate, controlling the leaking rate (or time constant) of the cell.
%It is not yet clear which aspects of the complicated architecture of LSTMs
%are really necessary. Memory cells are a good way of allowing the
%backpropagated error derivatives to neither explode nor vanish, but they
%are not the only way.  For example, recurrent nets with rectified linear
%hidden units that use the non-linear function $y=max(0,x)$ are much simpler
%than LSTMs and if the recurrent weight matrix is initialized to be close to
%the identity matrix they work about as well as LSTMs both for toy problems
%involving very long-range temporal structure and for real tasks like
%predicting the next word in text\citep{LeHinton}.

@@

\begin{figure}[ht]
\fbox{
\begin{minipage}{\textwidth}
\centerline{
\includegraphics[width=0.89\linewidth]{}
}
\caption{
}
\end{minipage}
}
\label{fig:imagenet-outputs}
\end{figure}
